### 2021-07-21 paper.tex
introduction complete

>>>>

	\subsection[scope of work]{Scope of Work}
	\subsubsection[deliverables]{Deliverables}
	\begin{itemize}
		\item Working program to take an MRI scan as input and predict presence
			of tumorous cells with $\geq 90\%$ accuracy.
	\end{itemize}

	\subsubsection[scope]{Scope}
	\begin{itemize}
		\item The working program has external dependencies ( libraries ) and
			it's expected to have a them installed for the program to work.
	\end{itemize}

	\subsubsection[timeline]{Timeline}
	\begin{itemize}
		\item \textbf{April 27, 2021} Project Assigned
		\item \textbf{May 2, 2021} Project finalized by supervisor, and group is
			divided into groups of two.
		\item \textbf{May 3, 2021} Data collection started.
		\item \textbf{May 12, 2021} Project Repository created and coding is
			started.
		\item \textbf{July 7, 2021} Coding is finished, documentation is
			started.
		\item \textbf{Just 21, 2021} Documentation complete.
	\end{itemize}

	\subsubsection[reports]{Reports}
	\begin{itemize}
		\item Constantly updating and pushing code to repository.
		\item Both teams staying in touch with each other to keep up with each
			others progress.
		\item Report back to supervisor every once a week.
	\end{itemize}
